opXRD: Open Experimental Powder X-ray Diffraction Database

### 2024-11-21 chapters/00_abstract.tex
Added subsections in dataset paragraphs

Powder X-ray diffraction (pXRD) experiments are a cornerstone for materials structure characterization.
Despite their widespread application, the analysis of pXRD diffractograms still presents a significant challenge to automation and thus a bottleneck in high-throughput experimentation automated materials discovery in self-driving labs.
Machine learning has emerged as a promising research direction to resolve this bottleneck by enabling automated powder diffraction data analysis.
A notable difficulty in applying machine learning to this domain is the lack of sufficiently sized experimental datasets, which has relegated machine learning researchers to train primarily on simulated data. Since simulations largely fail to accurately reflect the experiment, the performance of models trained on only simulated data often lacks transferability to experimental data and thus fails to provide value in practice.
With the Open Experimental Powder X-Ray Diffraction Database (opXRD), we aim to remedy this by providing an openly available and easily accessible dataset of partially labeled experimental powder diffractograms, providing machine learning researchers with a large quantity of real experimental diffractograms collected from a broad range of samples.
We provide almost barrier-free software tools that allow experimental researchers to find their data and make it accessible - in virtually any widely used format.
We collected XXX labeled and YYY unlabeled diffractograms from a wide spectrum of materials classes, which establishes the first version of the opXRD database.
We hope that this ongoing effort can guide machine learning research toward fully automated analysis of pXRD data and thus enable future self-driving materials labs.

>>>>

Powder X-ray diffraction (pXRD) experiments are a cornerstone for materials structure characterization.
Despite their widespread application, the analysis of pXRD diffractograms still presents a significant challenge to automation and thus a bottleneck in high-throughput experimentation automated materials discovery in self-driving labs.
Machine learning has emerged as a promising research direction to resolve this bottleneck by enabling automated powder diffraction data analysis.
A notable difficulty in applying machine learning to this domain is the lack of sufficiently sized experimental datasets, which has relegated machine learning researchers to train primarily on simulated data. Since simulations largely fail to accurately reflect the experiment, the performance of models trained on only simulated data often lacks transferability to experimental data and thus fails to provide value in practice.2
With the Open Experimental Powder X-Ray Diffraction Database (opXRD), we aim to remedy this by providing an openly available and easily accessible dataset of partially labeled experimental powder diffractograms, providing machine learning researchers with a large quantity of real experimental diffractograms collected from a broad range of samples.
We provide almost barrier-free software tools that allow experimental researchers to find their data and make it accessible - in virtually any widely used format.
We collected XXX labeled and YYY unlabeled diffractograms from a wide spectrum of materials classes, which establishes the first version of the opXRD database.
We hope that this ongoing effort can guide machine learning research toward fully automated analysis of pXRD data and thus enable future self-driving materials labs.

### 2024-11-21 chapters/01_introduction.tex
Added subsections in dataset paragraphs

% Manual vs (ML) automated Refinement
Employing manually operated Rietveld refinement, including determining a good initial structure for the optimization, is not without issues.
It is certainly not scalable to the degree required to keep up with advances in throughput and efficiency in other steps of the experimentation pipeline.
Automation of the Rietveld refinement requires the automation of finding initial guess structures, which is highly non-trivial, and the automation of the iterative optimization procedure, which can be done using black-box optimization algorithms \cite{Ozaki2020}. 
Initial guesses for Rietveld refinement are often obtained by matching the observed diffractogram to patterns from a database. Commonly used databases include the Powder Diffraction File\cite{GatesRector2019}, the Inorganic Crystal Structure Database \cite{Belsky2002}, and the Crystallography Open Database \cite{Grazulis2009}. An initial guess obtained from such a database is by no means guaranteed to lead to an accurate structure solution, even if it is iteratively revised, either manually or using blackbox optimization.\cite{Ozaki2020} Especially for novel observed structure types, simply matching to a database of known structures will not yield good results. Therefore, more complex crystal structure solution approaches need to be applied to find suitable crystal structure guesses. \\

@@

% Predicting structure information with machine learning
Models trained on datasets with simulated diffractograms have already shown very strong performance in predicting lattice parameters\cite{Dong2021, Chitturi2021, Habershon2004}, spacegroup \cite{Schopmans2023, Oviedo2018, Park2017, Vecsei2018, Zaloga2020, Suzuki2020, Chakraborty2021}, and crystallite size \cite{Dong2021, Chakraborty2021} from simulated diffractograms.
However, the performance substantially drops off when these models are applied to data originating from experiments \cite{Schopmans2023}[cite 2-3 papers, incl. ours].
The patterns observed in experiments suffer from a host of imperfections that need to be modeled accurately in order to be able to transfer models trained on simulated data to experimental patterns. This includes noise, background, preferred orientation of the sample, ...
Most approaches currently model these imperfections as a simple signal based on a heuristic functional form added to the simulated diffractograms.

>>>>

% Manual vs (ML) automated Refinement
Manually performing Rietveld refinement is time-consuming and often requires expert knowledge. It is not scalable to the degree required to keep up with advances in throughput and efficiency in other steps of the experimentation pipeline. In a Rietveld refinement process, the operator starts by setting parameters that characterize the background and peak shape of the powder diffraction pattern and determining a crystal structure from which the optimization process can start. The latter is usually done using search-match software, which identifies crystal structures with similar powder diffraction patterns from a database of crystal structures with accompanying powder diffraction patterns. However, attempting to refine all crystal structure parameters at once, starting from this initial structure, is known to lead to unphysical results. What makes the refinement process time-consuming and difficult is finding the correct order in which to refine the crystal structure parameters. \cite{Ozaki2020}  Additionally, if the fit develops into an unphysical set of parameters in this iterative determination of parameters, the operator must intervene to backtrack to the last step. \\

Commonly used databases for obtaining a match include the Powder Diffraction File\cite{GatesRector2019}, the Inorganic Crystal Structure Database \cite{Belsky2002}, and the Crystallography Open Database \cite{Grazulis2009}. An initial guess obtained from such a database is by no means guaranteed to lead to an accurate structure solution, even if it is iteratively revised, either manually or using blackbox optimization.\cite{Ozaki2020} Especially for novel observed structure types, simply matching to a database of known structures will not yield good results. Therefore, more complex crystal structure solution approaches need to be applied to find suitable crystal structure guesses. \\

@@

% Predicting structure information with machine learning
Models trained on datasets with simulated diffractograms have already shown very strong performance in predicting lattice parameters\cite{Dong2021, Chitturi2021, Habershon2004, zhang2024crystallographic}, spacegroup \cite{Schopmans2023, Oviedo2018, Park2017, Vecsei2018, Zaloga2020, Suzuki2020, Chakraborty2021,zhang2024crystallographic}, and crystallite size \cite{Dong2021, Chakraborty2021} from simulated diffractograms.
However, the performance substantially drops off when these models are applied to data originating from experiments \cite{Schopmans2023,zhang2024crystallographic}[cite 2-3 papers, incl. ours].
The patterns observed in experiments suffer from a host of imperfections that need to be modeled accurately in order to be able to transfer models trained on simulated data to experimental patterns. This includes noise, background, preferred orientation of the sample, ...
Most approaches currently model these imperfections as a simple signal based on a heuristic functional form added to the simulated diffractograms.

### 2024-11-21 chapters/02_existing_datasets.tex
Added subsections in dataset paragraphs

\item \textbf{Crystallography Open Database:}\footnote{More information on the crystallography open database can be found under \url{https://www.crystallography.net/cod/}.} The Crystallography Open Database (COD) is an open-access collection of crystal structures. It provides over 300.000 crystal structures in the form of .cif files. Of these files, 1063 contained the experimental powder diffraction data that was used to determine the underlying crystal structures of the investigated samples.

\item Scattered experimental datasets on Zenodo (TODO: roughly estimate size)
\item RRUFF
\item ...
\end{itemize}

>>>>

\item \textbf{Crystallography Open Database:}\footnote{More information on the crystallography open database can be found under \url{https://www.crystallography.net/cod/}.} The Crystallography Open Database (COD)\cite{Graulis2009cod} is an open-access collection of crystal structures. It provides over 500.000 crystal structures in the form of .cif files. Of these files, 1063 contained the experimental powder diffraction data that was used to determine the underlying crystal structures of the investigated samples.

\item Scattered experimental datasets on Zenodo (TODO: roughly estimate size)
\item \textbf{RRUFF}: The RRUFF Mineral Database \cite{Armbruster2015} provides detailed information on minerals, including their chemical compositions, crystallography, and spectroscopic data. Managed by the University of Arizona, it was created to serve as a public repository for mineral identification and research. It contains \num{908} distinct structures with experimental x-ray diffraction patterns.
\item ...
\end{itemize}

### 2024-11-21 chapters/03_SOTA_ML.tex
Added subsections in dataset paragraphs

Using simulated diffractograms based on structures from the ICSD, Lee et al. managed to train a deep convolutional neural network (CNN) that is able to classify occurring phases in diffractograms of a specific compound pool. \cite{Lee2020} Building upon their work they also developed models based on fully convolutional neural networks and transformer encoders, that predict the crystal system and the spacegroup and other structural properties, such as the band gap \cite{Lee2022}. With their best model for the crystal system prediction on ICSD structures, they achieved a test accuracy of \SI{92.2}{\percent}.
Park et al. reached a test accuracy of roughly 81\% for a CNN, which classifies space groups of simulated single-phase diffractograms. \cite{Park2017}
A regression analysis on lattice parameters within a broader framework encompassing all material classes was conducted by Chitturi et al.\cite{Chitturi2021} They developed a distinct CNN for each crystal system, utilizing a merged dataset from both the ICSD and the Cambridge Structural Database, and managed to achieve a mean absolute percentage error of about \SI{10}{\percent} for the lattice lengths, although they encountered difficulties in accurately predicting angles.

@@

TODO: briefly discuss papers about multiphase classification and remixing of diffraction patterns
Non-negative Matrix Factorization 2018: https://link.springer.com/chapter/10.1007/978-3-319-93031-2_4
non-negative matrix factorization 2018: https://ojs.aaai.org/aimagazine/index.php/aimagazine/article/view/2785
Physically-informed Graph-based DRNet (PG-DRNet) 2023: https://ieeexplore.ieee.org/abstract/document/10459774/

@@

>>>>

Using simulated diffractograms based on structures from the ICSD, Lee et al. managed to train a deep convolutional neural network (CNN) that is able to classify occurring phases in diffractograms of a specific compound pool. \cite{Lee2020} Building upon their work they also developed models based on fully convolutional neural networks and transformer encoders, that predict the crystal system and the spacegroup and other structural properties, such as the band gap \cite{Lee2022}. With their best model for the crystal system prediction on ICSD structures, they achieved a test accuracy of \SI{92.2}{\percent}.
Park et al. reached a test accuracy of roughly 81\% for a CNN, which classifies space groups of simulated single-phase diffractograms. \cite{Park2017}
A regression analysis on lattice parameters within a broader framework encompassing all material classes was conducted by Chitturi et al.\cite{Chitturi2021} They developed a distinct CNN for each crystal system, utilizing a merged dataset from both the ICSD and the Cambridge Structural Database, and managed to achieve a mean absolute percentage error of about \SI{10}{\percent} for the lattice lengths, although they encountered difficulties in accurately predicting angles. Zhang and Cao et al.\cite{zhang2024crystallographic} introduce a convolutional self-attention neural network trained on simulated patterns to classify crystal types. Their model was tested on 23,073 unary, binary, and ternary inorganic crystal structures sourced from the Crystallography Open Database. The study observed a noticeable performance drop when the pretrained model was applied to real experimental patterns, as opposed to simulated data. However, their recent work \cite{cao2024simxrd} proposes using convolutional peak descriptors that consider the detector's geometry, which significantly reduces the performance gap in their benchmark tests.
The option of training purely on experimental diffractograms unfortunately is unfeasible because of the limited availability of labeled experimental diffractograms, but Salgado et al. \cite{Salgado2023} showed, that adding a fraction of experimental patterns to a simulated training dataset improves the performance on unseen experimental patterns. They used \SI{50}{\percent} of the experimental patterns contained in the RRUFF database and added those to their large simulated training set. Then they tested their model's performance on the other half of the RRUFF database and achieved a performance increase in the 230-way spacegroup classification accuracy of \num{11} percentage points compared to the same model only trained on simulated patterns.

@@

TODO: briefly discuss papers about multiphase classification and remixing of diffraction patterns
Non-negative Matrix Factorization 2018: \url{https://link.springer.com/chapter/10.1007/978-3-319-93031-2_4}
non-negative matrix factorization 2018: \url{https://ojs.aaai.org/aimagazine/index.php/aimagazine/article/view/2785}
Physically-informed Graph-based DRNet (PG-DRNet) 2023: \url{https://ieeexplore.ieee.org/abstract/document/10459774/}

@@

The ultimate goal of this ML technology is to make PXRD data identification practical for experimental use, whether for identifying space group symmetry or phase composition. However, the current volume of experimental PXRD patterns is insufficient to effectively train ML models, highlighting an urgent need for a comprehensive experimental PXRD database. To address this, two key approaches are essential. First, developing more sophisticated simulation methods to better approximate experimental patterns\cite{cao2024simxrd}. Second, creating an experimental database that enables transfer learning to bridge the gap between simulated and real-world data. The development of opXRD is particularly significant, as it will provide a comprehensive experimental benchmark for the community, allowing fair comparison of baseline models and accurate evaluation of their applicability in real experimental situations.

### 2024-11-21 chapters/04_our_dataset.tex
Added subsections in dataset paragraphs

In collaboration with several other institutions we have collected a dataset of diffractograms stemming from experiment, some of them labeled with corresponding structural information. \\
Currently, institutions that contributed to our dataset include:
\begin{itemize}
    \item Institute of Nanotechnology at Karlsruhe Institute of Technology
    \item University of Southern California
    \item Lawrence Berkeley National Laboratory
\end{itemize}

%% Paragraph by FX Coudert and Arthur Hardiagon
%% Chimie Paris Tech, PSL University, CNRS, Institut de Recherche de Chimie Paris, 75005 Paris, France

We extracted experimental pXRD data from the Crystallography Open Database (COD).\cite{Grazulis2009, Vaitkus2023}  The COD is, to our knowledge, the largest open-access collection of experimental crystal structures of organic, inorganic, metal-organic compounds and minerals, containing more than 500,000 entries.\footnote{Available online at \url{https://www.crystallography.net/cod/}} The data in the COD is placed in the public domain and licensed under the CC0 License. Of the entire COD database, 5432 structures (1\% of the database) contained at least one tag from the {CIF\_POW} dictionary, i.e., relating to powder diffraction studies --- which is expected, since most crystal structures are resolved from single crystal diffraction. From these 5432 files, most contained only metadata related to the powder diffraction experiment, but did not include the raw data of the pattern itself. We could extract raw, experimental pXRD patterns from 1063 files in total, after curation of a small number of files with clearly invalid data.

The pXRD data from the COD database are of high quality, with a median resolution of $\Delta(2\theta) = 0.013${\textdegree} and an average number of 9190 points measured per pattern. They span a wide chemical space, including organic, inorganic and hybrid structures, including 75 different elements of the periodic table.

%%

%% Institute of Theoretical Informatics, Karlsruhe Institute of Technology,
%Kaiserstr. 12, 76131 Karlsruhe, Germany

The X-ray diffraction data were collected on a Bruker D8 Advance (Cu Kα1 radiation, λ = 1.54056 Å). The samples were initially recorded for various research projects over the last ten years and were measured with different step sizes, times per step, and over different angle ranges, but all using Cu Kα1 radiation. The samples mostly contained transition metal oxides, sulfides, and fluorides. A major part of the research focused on high-entropy materials, which involved incorporating many different elements into single-phase structures, leading to peak shifts or phase separations. Most of those multicomponent complex materials appeared in various structures, including rock-salt, spinel, fluorite, perovskite, and delafossite, to name a few.The samples were almost always prepared in powder form; therefore, powder XRD was performed on samples with adjusted height. To improve statistics, the samples were rotated during the entire measurement. Some air-sensitive samples were measured using a transparent polymer dome for protection. This dome led to increased background noise over the first 20° and slightly decreased pattern resolution. The samples were prepared using various synthesis techniques, mostly solid-state or wet chemical syntheses, to obtain the desired structures. Consequently, particle size and crystallinity varied significantly. The sample set also includes samples that were not successfully measured or where phases could not be identified.

We are still in the process of growing the dataset and additional contributions are still very welcome. To find out more about how to contribute to this dataset, visit our website specially designed to collect this dataset, https://xrd.aimat.science .

>>>>

In collaboration with several other institutions we have collected a dataset of diffractograms stemming from experiment, some of them labeled with corresponding structural information.

\begin{itemize}
    \item Institute of Nanotechnology at Karlsruhe Institute of Technology
    \item University of Southern California
    \item Lawrence Berkeley National Laboratory
    \item Hong Kong University of Science and Technology (Guangzhou)
    \item Swiss Federal Laboratories for Materials Science and Technology
\end{itemize}

%% Paragraph by FX Coudert and Arthur Hardiagon
\subsection*{Chimie Paris Tech, PSL University}

We extracted experimental pXRD data from the Crystallography Open Database (COD).\cite{Grazulis2009, Vaitkus2023} The COD is, to our knowledge, the largest open-access collection of experimental crystal structures of organic, inorganic, and metal-organic compounds and minerals, containing more than 500,000 entries. \footnote{Available online at \url{https://www.crystallography.net/cod/}.} The data in the COD is placed in the public domain and licensed under the CC0 License. Of the entire COD database, 5432 structures 1\% of the database) contained at least one tag from the {CIF\_POW} dictionary, i.e., relating to powder diffraction studies --- which is expected, since most crystal structures are resolved from single crystal diffraction. Of these 5432 files, most contained only metadata related to the powder diffraction experiment, but did not include the raw data of the pattern itself. We could extract raw, experimental pXRD patterns from 1063 files in total, after curation of a small number of files with clearly invalid data. \\

The pXRD data from the COD database are of high quality, with a median resolution of $\Delta(2\theta) = 0.013${\textdegree} and an average number of 9190 points measured per pattern. They span a wide chemical space, including organic, inorganic, and hybrid structures, including 75 different elements of the periodic table.

%% Paragraph by Ben Breitung
\subsection*{Institute of Nanotechnology, KIT}

The X-ray diffraction data were collected on a Bruker D8 Advance (Cu K$\alpha$1 radiation, $\lambda$ = 1.54056 Å). The samples were initially recorded for various research projects over the last ten years and were measured with different step sizes, times per step, and over different angle ranges, but all using Cu K$\alpha$1 radiation. The samples mostly contained transition metal oxides, sulfides, and fluorides. A major part of the research focused on high-entropy materials, which involved incorporating many different elements into single-phase structures, leading to peak shifts or phase separations. Most of those multi-component complex materials appeared in various structures, including rock-salt, spinel, fluorite, perovskite, and delafossite, to name a few.The samples were almost always prepared in powder form; therefore, powder XRD was performed on samples with adjusted height. To improve statistics, the samples were rotated during the entire measurement. Some air-sensitive samples were measured using a transparent polymer dome for protection. This dome led to increased background noise over the first 20° and slightly decreased pattern resolution. The samples were prepared using various synthesis techniques, mostly solid-state or wet chemical syntheses, to obtain the desired structures. Consequently, particle size and crystallinity varied significantly. The sample set also includes samples that were not successfully measured or where phases could not be identified.

% Paragraph by Tim Kodalle
\subsection*{Lawrence Berkeley National Lab}

Experimental XRD data were collected at beamline 12.3.2 of the Advanced Light Source, the synchrotron at Lawrence Berkeley National Laboratory, using a photon energy of 10 keV (corresponding to a wavelength of $\lambda$ = 1.23984193 Å), selected using a Si(111) monochromator. Measurements were taken in grazing incidence geometry, i.e. using a beam incidence angle of 1$^{\circ}$. Two-dimensional diffraction images were recorded using a Dectris Pilatus 1M area detector at an angle between 34$^{\circ}$ and 36$^{\circ}$ with a sample-to-detector distance of roughly 190 mm. The two-dimensional data were calibrated using an Al$_{2}$O$_{3}$ calibration standard and integrated along the azimuthal angle. Data collection was performed in situ during thin-film deposition using a custom-made spin-coating and annealing stage. One dataset was collected spin-coating triple cation metal-halide perovskite precursor solutions with the composition Cs$_{0.05}$(MA$_{0.23}$FA$_{0.77}$)Pb$_{1.1}$(I$_{0.77}$Br$_{0.23}$)$_{3}$ (MA = Methylammonium, FA = Formamidinium) onto various substrates, including glass (amorphous), GaAs wafers (single crystalline) as well as stacks of glass/ITO, GaAs/Mo/Cu(In,Ga)Se$_{2}$/CdS/ZnO, and glass/Mo/Cu(In,Ga)Se$_{2}$/CdS/ZnO (glass/CIGS). Some of the substrates were additionally covered with a self-assembling monolayer of MeO-2PACz. The GaAs substrates were prepared by Dr. Jiro Nishinaga from the National Institute of Advanced Industrial Science and Technology (AIST) in Japan and the glass/CIGS substrates by Dr. Christian Kaufmann and his team at Helmholtz-Zentrum Berlin (HZB) in Germany. \\

A second dataset was collected from spin-coating metal-halide perovskite precursor solutions with varying compositions of \ce{MAPb(I_{1-x}Br_x)3} (where MA = Methylammonium and x = 0, 0.33, 0.5, 0.67, 1) spin-coated onto glass substrates. The substrates were preheated to different temperatures (30°C, 50°C, 70°C, and 90°C), and the spin-coating process was performed at a constant temperature on the preheated substrates. For both datasets, diffraction data were continuously measured during spin-coating, chemical induction of crystallization, and annealing of the samples (at 100$^{\circ}$C and 110$^{\circ}$C respectively) with a frequency of about 0.56 1/s and  0.54 1/s. Each in situ measurement consisted of about 500 to 1000 individual diffractograms. Depending on the substrate, each series of diffractograms shows an evolution from substrate only to a combination of polycrystalline perovskite, PbI$_{2}$ and substrate via several intermediate phases.

% Paragraph by Bin Cao
\subsection*{Guangzhou Municipal Key Laboratory of Materials Informatics, HKUST}

In the past two years, we established a small-scale experimental PXRD database called the X-Ray Phase Identification Public Experimental Dataset (XRed,  \href{https://github.com/WPEM/XRED}{https://github.com/WPEM/XRED}). The data in XRed is generated in our lab using instruments such as the Empyrean 3.0, Aeris, and Bruker D8 Advance diffractometers under copper targets. Hundreds of PXRD patterns have been refined, labeled with CIF files, and organized by elemental systems. The dataset includes original experimental files across single-phase to five-phase mixtures. This project is progressing toward integration with the comprehensive opXRD database to establish a large-scale, long-term experimental resource.

% Paragraph by Moritz Wolf and Tony-yi 
\subsection*{Institute of Catalysis Research and Technology, KIT}

X-ray diffraction (XRD) was conducted with an X’Pert Pro MPD (Panalytical) in Bragg-Brentano geometry using a copper X-ray source ($\lambda_{K_{\alpha}} = 1.5406 Å$). The patterns were acquired from 5-80° $2\theta$ with a step size of 0.016711° or 0.033420° and a total acquisition time of 40 to 120 min. A variety of samples were analyzed including commercial catalysts, bulk reference materials, porous metal oxide particles, and nanoparticles. The latter were synthesized via the surfactant-free benzyl alcohol route (10.1039/C9DT01634A, 10.1016/j.matchemphys.2018.04.021). The cobalt oxide (CoO or Co3O4) and cerium oxide (CeO2) nanoparticles were in the size range of 4-16 nm according to the Scherrer equation. A series of porous Al2O3 materials, which were prepared by calcination of boehmite (AlOOH) at various temperatures, represents crystalline samples with limited long-range structure and various contributions of Al2O3 polymorphs.

% Paragraph by Alexander Wieczorek and Sebastiann Siol
\subsection*{Laboratory for Surface Science and Coating Technologies, Empa}

XRD data was measured using a Bruker D8 Discover equipped with a Cu~K$\alpha$ radiation source ($\lambda$~=~1.54056~{\AA} for Cu~K$\alpha$\textsubscript{1} and $\lambda$~=~1.54439~{\AA} for Cu~K$\alpha$\textsubscript{2}) in a Bragg-Brentano geometry. For the reported data sets the instrument was equipped with a Goebel mirror effectively removing the Cu~K$\beta$ radiation. The data set originates from the combinatorial exploration of the Zn–V–N compositional space, as well as data gathered from multiple research activities on more established metal halide perovskite semiconductors. All data was collected from thin films deposited on borosilicate glass. The Zn–V–N films showed some preferential out of plane orientation, while for the perovskites the preferential orientation was minimal, resulting in the presence of all reflections.
Each combinatorial Zn–V–N library was synthesized using radio-frequency co-sputtering of Zn and V in a mixed Ar and N\textsubscript{2} plasma. An orthogonal deposition temperature and composition gradient was created, resulting in a deposition temperature of 220~{\textdegree}C for samples 1~–~9 and 114~{\textdegree}C for samples 37~–~45. The composition for each sample was determined using X-Ray fluorescence (XRF) spectroscopy which was further calibrated through Rutherford backscattering spectroscopy (RBS) based on selected samples. The newly identified and isolated semiconductor Zn\textsubscript{2}VN\textsubscript{3} was identified to exhibit a cation-disordered wurtzite structure as verified by additional GI-XRD and SAED measurements.\cite{Zhuk2021}
Tin halide perovskites were deposited using single-step spin-coating as reported elsewhere.\cite{Wieczorek2023} Methylammonium lead iodide libraries with varying degrees of residual PbI\textsubscript{2} were deposited using a two-step procedure involving both thermal evaporation of PbI\textsubscript{2} and subsequent spin-coating of a methylammonium solution. The relative phase fractions were quantified using supplementary azimuthal angle scans coupled with structural factors and geometrical factors as reported elsewhere.\cite{Wieczorek2024} Fully inorganic lead perovskite libraries were prepared using thermal co-evaporation of lead and cesium halide salts.
All metal halide perovskite libraries were measured within a custom-made X-Ray transparent inert-gas dome, resulting in the presence of minor additional features within the $\theta$~=~19~–~31{\textdegree} range. For all combinatorial libraries where any phases are specified, the complete set of phases are reported in the meta data.

We are still in the process of growing the dataset and additional contributions are still very welcome. To find out more about how to contribute to this dataset, visit our website specially designed to collect this dataset, \url{https://xrd.aimat.science} .

### 2024-11-21 chapters/05_how_to_use.tex
Added subsections in dataset paragraphs

A major advantage of this dataset over other comparable datasets is that it is very easy to handle in python and in PyTorch.
Our accompanying python library xrdpattern (https://github.com/aimat-lab/xrdpattern) provides a means to read in as much of the dataset as fits in memory simply by using PatternDB.load(data\_dirpath). The patterns attribute of this class is a list of the indivdual pattern diffractograms, each of which supports a standardize, plot and to tensor method. \\
The standardize method returns a "standardized" version of the pattern with a fixed angle range, a fixed number of entries and intensities normalized to the $[0,1]$ interval.

>>>>

A major advantage of this dataset over other comparable datasets is that it is very easy to handle in python and in PyTorch.
Our accompanying python library xrdpattern (\url{https://github.com/aimat-lab/xrdpattern}) provides a means to read the dataset simply by using PatternDB.load(data\_dirpath). The patterns attribute of this class is a list of the indivdual pattern diffractograms, each of which supports a standardize, plot and to tensor method. \\
The standardize method returns a "standardized" version of the pattern with a fixed angle range, a fixed number of entries and intensities normalized to the $[0,1]$ interval.

% caobin
We have launched Xqueryer (http://xqueryer.caobin.asia/), a free online platform for phase identification. Users can upload experimental PXRD data to identify and match structures from the Materials Project database. Uploaded data is stored and integrated into our opXRD database.

### 2024-11-21 main.tex
Added subsections in dataset paragraphs

\author[1,2]{Daniel Hollarek}
\author[1,2]{Henrik Schopmans}
\author[1,2]{Jona Östreicher}
\author[2]{Simon Schweidler}
\author[3]{Adie Alwen}
\author[4]{Mriganka Singh}
\author[4]{Tim Kodalle}
\author[2]{Ben Breitung}
\author[4]{Maged Abdelsamie}
\author[4]{Gregoire Heymans}
\author[4]{Hanlin Hu}
\author[5]{Alexander Wieczorek}
\author[5]{Siarhei Zhuk}
\author[5]{Sebastiann Siol}
\author[6]{Moritz Wolf}
\author[7]{Arthur Hardiagon}
\author[8]{Bin Cao}
\author[8]{Tong-yi Zhang}
\author[4]{Carolin Sutter-Fella}
\author[3]{Andrea Hodge}
\author[1,2]{Pascal Friederich}

@@

\affil[1]{Institute of Theoretical Informatics, Karlsruhe Institute of Technology, 76131 Karlsruhe, Germany}
\affil[2]{Institute of Nanotechnology, Karlsruhe Institute of Technology, 76131 Karlsruhe, Germany}
\affil[3]{Department of Chemical Engineering and Materials Science, University of Southern California, Los Angeles CA 90089, USA}
\affil[4]{Lawrence Berkeley National Laboratory, Molecular Foundry Division, Berkeley 94720 CA, USA}
\affil[5]{Empa-Swiss Federal Laboratories
for Materials Science and Technology, CH-8600 Dübendorf,
Switzerland}
\affil[6]{Engler-Bunte-Institut \& Institute of Catalysis
Research and Technology, Karlsruhe Institute of Technology, Karlsruhe, Germany}
\affil[7]{Chimie ParisTech, PSL University, CNRS, Institut de Recherche de Chimie Paris, 75005 Paris, France}
\affil[8]{Guangzhou Municipal Key Laboratory of Materials Informatics,  Hong Kong University of
Science and Technology (Guangzhou), Guangzhou 511400 Guangdong, China}

\begin{document}

@@

\subsection*{Acknowledgements}
We acknowledge financial support by the German Research Foundation (DFG) through the Research Training Group 2450 “Tailored Scale-Bridging Approaches to Computational Nanoscience”. We acknowledge support by the Federal Ministry of Education and Research (BMBF) under Grant No. 01DM21001B (German-Canadian Materials Acceleration Center). We acknowledge financial support from the Helmholtz Foundation Model Initiative within Project "SOL-AI".

>>>>

\author[1,2]{Daniel Hollarek}
\author[1,2]{Henrik Schopmans}
\author[1,2]{Jona Östreicher}
\author[2]{Simon Schweidler}
\author[3]{Adie Alwen}
\author[4]{Mriganka Singh}
\author[4,5]{Tim Kodalle}
\author[2]{Ben Breitung}
\author[11, 12]{Maged Abdelsamie}
\author[6]{Gregoire Heymans}
\author[7]{Alexander Wieczorek}
\author[7]{Siarhei Zhuk}
\author[7]{Sebastian Siol}
\author[8]{Moritz Wolf}
\author[9]{François-Xavier Coudert}
\author[9]{Arthur Hardiagon}
\author[10]{Bin Cao}
\author[13]{Ruth Schwaiger}
\author[10]{Tong-yi Zhang}
\author[4]{Carolin M. Sutter-Fella}
\author[3]{Andrea M. Hodge}
\author[1,2]{Pascal Friederich}

@@

\affil[1]{Institute of Theoretical Informatics, Karlsruhe Institute of Technology, 76131 Karlsruhe, Germany}
\affil[2]{Institute of Nanotechnology, Karlsruhe Institute of Technology, 76131 Karlsruhe, Germany}
\affil[3]{Department of Chemical Engineering and Materials Science, University of Southern California, Los Angeles CA 90089, USA}
\affil[4]{Lawrence Berkeley National Laboratory, Molecular Foundry Division, Berkeley 94720 CA, USA}
\affil[5]{Lawrence Berkeley National Laboratory, Advanced Light Source, Berkeley 94720 CA, USA}
\affil[6]{Lawrence Berkeley National Laboratory, Chemical Sciences Division, Berkeley 94720 CA, USA}
\affil[7]{Empa~–~Swiss Federal Laboratories
for Materials Science and Technology, 8600 Dübendorf,
Switzerland}
\affil[8]{Engler-Bunte-Institut \& Institute of Catalysis
Research and Technology, Karlsruhe Institute of Technology, Karlsruhe, Germany}
\affil[9]{Chimie ParisTech, PSL University, CNRS, Institut de Recherche de Chimie Paris, 75005 Paris, France}
\affil[10]{Guangzhou Municipal Key Laboratory of Materials Informatics,  Hong Kong University of
Science and Technology (Guangzhou), Guangzhou 511400, China}
\affil[11]{Material Science and Engineering Department, King Fahd University of Petroleum and Minerals (KFUPM), Dhahran 31261, Saudi Arabia}
\affil[12]{Interdisciplinary Research Center for Intelligent Manufacturing and Robotics, KFUPM, Dhahran 31261, Saudi Arabia}
\affil[13]{Institute of Energy Materials and Devices, Forschungszentrum Juelich GmbH, 52425 Juelich, Germany}
\begin{document}

@@

\subsection*{Acknowledgements}
We acknowledge financial support by the German Research Foundation (DFG) through the Research Training Group 2450 “Tailored Scale-Bridging Approaches to Computational Nanoscience”. We acknowledge support by the Federal Ministry of Education and Research (BMBF) under Grant No. 01DM21001B (German-Canadian Materials Acceleration Center). We acknowledge financial support from the Helmholtz Foundation Model Initiative within Project "SOL-AI". Part of this work was funded under the France 2030 framework by Agence Nationale de la Recherche (project ANR-22-PEXD-0009 of PEPR DIADEM). Work at the Molecular Foundry was supported by the Office of Science, Office of Basic Energy Sciences, of the U.S. Department of Energy under Contract No. DE-AC02-05CH11231. Work at the Advanced Light Source (ALS) was done at beamline 12.3.2. The ALS is a DOE Office of Science User Facility under contract no. DE-AC02-05CH11231. The development of the online phase identification platform is supported by the Guangzhou-HKUST(GZ) Joint Funding Program (No. 2023A03J0003). Work by the USC group was supported by the National Science Foundation (NSF) grant numbers DMR-2227178 and OISE-2106597.

%TODO: Include acknowledgements to the following researchers from the Wolf group
%The author list is fine, unfortunately I did not get real support from my team to provide a bigger consistent dataset. Please acknowledge the experimental contributions of Angelina Barthelmeß, Elisabeth Herzinger, Henning Hinrichs.
